\documentclass[fleqn,12pt]{article}

\usepackage[a4paper,includehead,nomarginpar]{geometry}
\usepackage[affil-it]{authblk}
\usepackage[shortlabels]{enumitem}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{fancyhdr}
\usepackage{fancyvrb}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{hyperref}
\usepackage{latexsym}
\usepackage{minted}
\usepackage{times}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
    linkcolor=blue,
    filecolor=magenta,
    pdftitle={Kyle Crusius}
}

\setlength{\headsep}{15pt}
\setlength{\headheight}{15pt}
\setlength{\topmargin}{0pt}
\setlength{\parskip}{12pt}

\pagestyle{fancy}
\fancyhead{}
\lhead{CSCE 312: Computer Organization}
\rhead{Texas A\&M University}
\fancyfoot{}
\cfoot{\thepage}

\title{\vspace{-2.5cm}Lab 6 Individual Report}
\author{
    Kyle Crusius | 428003578
}
\affil{Texas A\&M University}
\date{\vspace{-28pt}13 December 2022}

\begin{document}
\maketitle
\begin{center}
\vspace{-42pt}
\rule{\textwidth}{.1pt}
{\large
An Aggie does not lie, cheat or steal.\\
Nor does an Aggie tolerate those who do.
}
\end{center}
\begin{center}
Group Members:\\
Huy Lai | 132000359\\
Arjun Kurkal | 631004597\\
Vishnu Naidu | 630003015
\end{center}

\section*{My Contribution}
\begin{enumerate}
    \item Decode
    \item Document Management/Oversight 
    \item Mild Debugging (See Huy and Arjun for Higher-Tier Debugging)
\end{enumerate} 

\section*{Advantages and Disadvantages}
Working in a group significantly improved the individual workload and made it easier to get help. \\\\
Due to the complexity of the project, it was not sufficient to specialize in one area of the work. It would be difficult to meaningfully contribute without having a hand in every stage, which makes the group aspect harder to collaborate. \\\\
Overall, the project was manageable, but I would like to see more detailed demos in the future.

\section*{Best Design}
Huy's Fetch Stage design was the most efficient. Along with his Write Back and PC Update.
Arjun's Execute was also efficient.
\end{document}  